# Communicable, Maternal, Neonatal, and Nutritional Disease Burden (CMNN)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the communicable diseases data
data_cmnn <- read_csv(here("data/burden-of-disease-cmnn.csv")) %>% 
  rename(daly_cmnn = `DALYs (Disability-Adjusted Life Years) - Communicable, maternal, neonatal, and nutritional diseases - Sex: Both - Age: Age-standardized (Rate)`)
```

```{r}
# Filter the dataset to include only the three countries chosen by your group.
data_cmnn_filtered <- data_cmnn %>% 
  filter(Entity %in% c("Germany", "Canada", "India"))
```

## Table of Estimates for CMNN Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data to show each country in a separate column.
data_cmnn_wide <- data_cmnn_filtered %>% 
  select(-Code) %>% 
  pivot_wider(names_from = Entity, values_from = daly_cmnn)
# Use kable() from the knitr package to render the table.

kable(data_cmnn_wide)
```

## Plot Showing Trends in CMNN Burden Over Time

```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.

data_cmnn_filtered %>% 
  ggplot(aes(x = Year, y = daly_cmnn, group = Entity, col = Entity))+
  geom_line()+
  scale_y_log10()
```

## Summary of CMNN Burden Findings
The DALY CMNN burden has decreased between 1990 and 2019 in all three countries analyzed. Whereas Germany and Canada had a rather low DALY CMNN of under 2000 in 1990, it was over 30,000 in India. While the score decreased constantly in India in Germany, there is a plateau in Canada from 1990 to 1995, with a decrease afterwards.
