# Overall Disease Burden

```{r include=FALSE}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the overall disease data
data_overall <- read_csv(here("data/burden-of-disease-all-causes.csv"))
```

```{r include=FALSE}
data_filtered <- data_overall %>% 
  filter(Entity %in% c("Canada","Germany", "India"))

data_filtered <- data_filtered %>% janitor::clean_names()

data_filtered <- data_filtered %>% 
  rename(daly = dal_ys_disability_adjusted_life_years_all_causes_sex_both_age_age_standardized_rate)
```


## Table of Estimates for Overall Disease Burden Over Time

```{r echo=FALSE}
# Here render a table for the DALY burden over time for the three countries. 
# You should pivot the data to show each country in a separate column.
# Use kable() from the knitr package to render the table.

data_wide <- data_filtered %>% 
  select(-code) %>% 
  pivot_wider(
    names_from = entity,
  values_from = daly
  )

kable(data_wide)
```

## Plot Showing Trends in Overall Disease Burden Over Time

```{r echo=FALSE}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.

ggplot(data_filtered,
       mapping = aes(x = year,
                     y = daly,
                     colour = entity)) +
  geom_line() +
  scale_y_log10()
```

## Summary of Overall Disease Burden Findings

The chart illustrates a consistent decline in Disability-Adjusted Life Years (DALYs) from 1990 to 2020 for Canada, Germany, and India. India shows the highest DALYs but also the most significant reduction over time, indicating substantial health improvements. In contrast, Canada and Germany have lower DALYs, with more gradual decline.